### 2023-07-21 ms.qmd
Throw out prose

---
abstract: "***Abstract*** Although video games receive immense attention as potential carriers of both positive and negative psychological effects, empirical evidence on games' effects remains mixed. One reason for this, we believe, is that the effects of games---if any---might be short lived and transient. To capture potential effects of games during play itself, we queried XXX players mood at the start of XXX gameplay sessions and in XXX subsequent moods. Critically, mood was reported in game in a modified version of a commercially available game. We found X Y and Z but surprisingly not XYZ. Implications. Statements."
date: 2023-07-18
bibliography: bibliography.bib
format:
  docx:
    reference-doc: reference.docx
  pdf:
    keep-tex: false
    documentclass: scrartcl
    classoption: twocolumn
    fontfamily: libertinus
    fontsize: 10pt
    papersize: a4
    fig-align: center
    fig-width: 8
    section-number: true
    geometry:
      - top=20mm
      - left=20mm
      - right=20mm
      - bottom=30mm
    include-in-header:
      - text: |
          \setlength{\columnsep}{7.5mm}
          \addtokomafont{disposition}{\normalfont}
---

@@

# Introduction

## Current study

Here, we ask how players' mood changes during gameplay sessions.

@@

## Procedure

Describe PWS.

>>>>

---
date: 2023-07-18
bibliography: bibliography.bib
format:
  docx:
    reference-doc: reference.docx
  pdf:
    keep-tex: false
    documentclass: scrartcl
    classoption: twocolumn
    fontfamily: libertinus
    fontsize: 10pt
    papersize: a4
    fig-align: center
    fig-width: 8
    section-number: true
    geometry:
      - top=20mm
      - left=20mm
      - right=20mm
      - bottom=30mm
    include-in-header:
      - text: |
          \setlength{\columnsep}{7.5mm}
          \addtokomafont{disposition}{\normalfont}
---

@@

@@
